Class files control the formatting and presentation of documents. The class files currently available include:
\begin{description}
\item[CorporateReport.cls]{compiles the document using the LaTeX \emph{report} class, with corporate formatting. This is intended for longer documents and allows the use of chapters.}
\item[CorporateArticle.cls] compiles the document using the LaTeX \emph{article} class, with corporate formatting. This is intended for shorter documents such as journal articles. This class does not support the use of chapters.
\item[CorporateResources.tex] contains the common packages and formatting descriptions that are implemented by the \emph{CorporateReport.cls} and \emph{CorporateArticle.cls} classes.
\end{description}

As with normal classes, options are passed to the class in the \verb+\documentclass+ line:

\begin{lstlisting}
\documentclass[option 1, ..., option n]{CorporateArticle}
\end{lstlisting}

All of the usual options can be used with the \emph{Corporate*.cls} classes, including \emph{twocolumn, letterpaper,} and so-on.

Options specific to \emph{Corporate*.cls} include:
\begin{description}
\item[draft]{add a `draft' watermark to all pages.}
\item[blacklinks]{make all links the same color as the rest of the body text.}
\end{description}

The \emph{Corporate....cls} files call a variety of other packages. Packages are codes that modify the appearance or behaviour of LaTeX to achieve something. Table \ref{Tab:Packages} lists the packages that are explicitly called by \emph{Corporate*.cls} or \emph{CorporateResources.tex} in the order they are called in. These packages often call other packages, so this is not an exhaustive list.

\begin{table*}[!ht]
\centering
\caption[Packages loaded by the Corporate classes]{Packages loaded by the Corporate classes.}
\label{Tab:Packages}
\begin{tabular*}{\textwidth}{llp{0.6\textwidth}}
\toprule
Package & Options & Functionality\\
\midrule
%accessibility & tagged & generates the document structure and tagging \\
amsfonts, amssymb & & supplies AMS fonts, which are useful for mathematics \\
babel & english & activates language-appropriate hyphenation rules\\
booktabs & & improves the formatting of tables \\
caption & & required to generate captions for floats\\
courier& & changes fonts \\
fontenc & T1 & enables direct typing of international characters \\
geometry & & sets page size and margins \\
graphicx & & graphics handling, including \emph{.eps} figures \\
hyphenat & & improves spacing and breaking of hyphenated words \\
listings & & enables the inclusion of high-quality computer code listings\\
mathptmx& & changes fonts \\
nag & & checks that packages are up to date and looks for bad habits in LaTeX code\\
opensans& scaled=0.95 & sets Google's \emph{Open Sans} as the default font\\
parskip & & required for better spacing\\
pdfcomment & & required for tool-tips. Also calls the \texttt{hyperref} package.\\
setspace & & required for better spacing\\
subcaption & & provides the \texttt{subfigure} environment to produce sub figures \\
tocloft & & improved table of contents and list of figures/tables in memoir documents\\
tocbibind & nottoc, notlot, notlof & Adds bibliography, index, and contents entries to the Table of Contents in memoir documents\\
todonotes & & inline and margin to-do notes \\
xcolor & & Driver-independent color extensions for LaTeX and pdfLaTeX\\
\bottomrule
\end{tabular*}
\end{table*}

It should be noted that the `english` option to Babel really means \emph{American} English.
